Guidelines and Policy for Surveys using \SW

### 2014-05-13 doc/sw-publication-policy-cfhtls.tex
Updated Policy and Author .tex files

The \sw website is designed to motivate and  enable tens of thousands of
people to perform the scientific tasks of strong gravitational lens
identification and classification.  The \sw collaboration comprises the
sum total of the volunteers who have logged in and contributed
classifications to the project. (We would include those who did not
log in as well, but we don't know who they are.) This means that the
minimal requirement for \sw collaboration membership is classification with a Zooniverse ID,
and some contribution on the site (\ie classifying, or discussing
Subjects in \Talk \footnote{\Talk (found at talk.spacewarps.org) is a forum for \sw collaborators to discuss individual sources and the \sw project in general. Bugs can also be reported. This is the direct portal for communication with the \sw community.}).

@@

\item{\bf Zooniverse:} \sw development team (led by
A.\,Kapadia).

\item{\bf Science Team:} This is a core group of scientists, both citizen and
professional, that helped to design, build and test the \sw website
and the initial CFHT-LS project. The Science Team includes the PIs.

@@

In the remaining sections we look at the various publications that might
arise from the \sw project, and suggest reasonable guidelines for
deciding on their authorship.

@@

\section{The \SW Paper Series}
\label{sec:series}

@@

\begin{itemize}
\item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
\item \sw II: The \sw  simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis. 
\item \sw III: The first new candidates from CFHT-LS \textit{including models, follow-up if feasible}
\item \sw IV: The results from CFHT-LS search including the comparison and analysis of citizen scientist classification versus lens-finding algorithms (maybe split into smaller papers).
\end{itemize}

@@

@@

\noindent The author categories are grouped according to collaboration membership (defined above). These groups of authors have either the status to ``opt-out'' or "on contribution" of \sw publications.  ``Opt-out'' means the listed people are authors by default and must explicitly state if they wish for their names to be removed from \sw publications. ``On contribution'' means the people listed are invited to comment on and contribute to publications. The Principal Investigators, Zooniverse development team and \sw Science team all have opt-out status and the \sw Affiliates have on contribution status.

The first author of any \sw paper will decide, as
usual, on the author list of their own paper. This will include adding Affiliates who they think have made a substantial contribution to that investigation, as well as inviting
scientists from outside the list of \sw authors, or from outside the
collaboration.  The PIs will act as adjudicators if any disputes arise,
but to be honest we are not expecting any.

Lead authors of \sw papers should circulate drafts to the list of \sw authors (according to the policy above) and allow a minimum of two weeks to give time for comments and to opt-in. If  ``on contribution'' authors have not provided comments within this time frame they will not be included as authors on the paper. If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.

@@

Any \sw series and \sw enabled discovery papers should include
\begin{itemize}
\item citations to the \sw system papers, \sw I \& II
\item the collaboration should be acknowledged in the acknowledgement section with a link to the collaboration membership page (URL: to be added).
\end{itemize}

@@

\appendix
\section{Current Author List: author.tex}
\label{sec:appa}
{\small \verbatiminput{./authors.tex}}

>>>>

The \sw website is designed to motivate and  enable tens of thousands of
people to perform the scientific tasks of strong gravitational lens
identification and classification.  The \sw collaboration comprises the
sum total of the volunteers who have logged in and contributed
classifications to the project (we would include those who did not
log in as well, but we don't know who they are!). This means that the
minimal requirement for \sw collaboration membership is logging in with a Zooniverse ID
and providing some contribution on the site (\ie classifying, or discussing
Subjects in \Talk \footnote{\Talk (found at talk.spacewarps.org) is a forum for \sw collaborators to discuss individual sources and the \sw project in general. Bugs can also be reported. This is the direct portal for communication with the \sw community.}).\\

@@

\item{\bf Zooniverse:} \sw development team (originally led by
A.\,Kapadia).

\item{\bf Science Team:} This is a core group of scientists, both citizen and
professional, that helped to design, build and test the \sw website
and the initial CFHT-LS project. The Science Team includes the \sw PIs.

@@

@@

\section{The \SW Papers}

In the following sections we look at the various publications that might
arise from the \sw project, and suggest reasonable guidelines for
deciding on their authorship.

\subsection{The \sw System Paper Series}
\label{sec:series}

@@

\begin{itemize}
\item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
\item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates. 
\item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
\item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
\item \sw X: New lenses(s) in \sw (authored by collaboration members)
\end{itemize}

@@

\subsection{\sw Related Papers}
These are \sw related papers but do not necessarily fall into the \sw paper series
\begin{itemize}
\item Lens modelling in \sw (Spaghetti Lens)
\item New lenses(s) in \sw (authored by persons not part of the \sw collaboration)
\end{itemize}

@@

\noindent The author categories are grouped according to collaboration membership (defined above). These authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names.

The Principal Investigators, Zooniverse development team and \sw Science team all have ``opt-out'' status and the \sw Affiliates have ``opt-in'' status.

The first author of any \sw paper will decide, as usual, on the author list of their own paper. This will include adding Affiliates who they think have made a substantial contribution to that investigation, as well as inviting scientists from outside the list of \sw authors, or from outside the
collaboration.  The \sw PIs will act as adjudicators if any disputes arise, but to be honest we are not expecting any.

Lead authors of \sw papers should circulate drafts to the list of \sw authors (according to the policy above) and allow a minimum of two weeks to give time for comments. If  ``opt-in'' authors have not provided comments within this time frame they will *not* be included as authors on the paper. If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.

For \sw related papers, the \sw PIs should be contacted for a suggested minimum contingent of collaboration authors to be added to the paper. These papers are treated with the same status as the general \sw Please also refer to the general \sw policy document

@@

Any \sw series and \sw enabled discovery papers should include
\begin{itemize}
\item citations to the \sw system papers, \sw I \& II
\item the collaboration should be acknowledged in the acknowledgement section with a link to the collaboration membership page (URL: to be added).
\item \sw CFHT-LS is based on data processed by CFHT-LS and Terapix, so please add the following acknowledgement to your paper:\\
\textit{``Based on observations obtained with MegaPrime/MegaCam, a joint project of CFHT and CEA/IRFU, at the Canada-France-Hawaii Telescope (CFHT) which is operated by the National Research Council (NRC) of Canada, the Institut National des Science de l'Univers of the Centre National de la Recherche Scientifique (CNRS) of France, and the University of Hawaii. This work is based in part on data products produced at Terapix available at the Canadian Astronomy Data Centre as part of the Canada-France-Hawaii Telescope Legacy Survey, a collaborative project of NRC and CNRS.''}\\
from http://www.cfht.hawaii.edu/Science/CFHLS/cfhtlspublitext.html

\end{itemize}

@@

\appendix
\section{Current Author List for \sw series papers: author.tex}
\label{sec:appa}
{\small \verbatiminput{authors.tex}}

### 2014-05-13 doc/sw-publication-policy-gen.tex
Updated Policy and Author .tex files

\sw is a public website. All images displayed there are by definition in the
public domain, and so must be expected to be downloaded, copied and
redistributed by any \sw user. This is a \textbf{good thing}: images of the sky taken
with publicly-funded telescopes belong to everyone. It is the responsibility
of the SSTs to provide images in a way that is consistent
with their own data access rules. There are two things that SSTs can
do to in order to respect any proprietary period that they have imposed on
themselves:
\begin{enumerate}

@@

There is a reasonable amount of work in preparing data and images for delivery to \sw. The \sw team will provide assistance to future teams in data preparation. We hope the benefits of using the \sw service will far outweigh the time needed to prepare data.

\subsection{Future Project Proposals}
Any future \sw projects are requested to liaise with the PIs regarding their project. We ask that potential project teams first approach the PIs (Marshall, Verma, More) with a short description of their project that includes the following information.

@@

The original \sw papers by definition, provide a complete description of the system, and its results from the CFHTLS survey. The science team of
any other survey (such as DES, RCS, KIDS, PS1, HSC \etc) should be able
to read these papers before designing their own \sw project, and cite them as justification for some of their decisions. As the \sw paper series appears links to the papers will be given in this draft. Prior to publications, draft papers can also be shared on request by the \sw PIs (\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com})

@@

Implementing a new project based on different survey data will require support from the \sw Science Team, in three
respects: 
\begin{enumerate}

\item In {\bf preparing data} for the site, and uploading it onto the
Zooniverse servers. The \sw Science Team can advise on suitable Training
Subjects and image display settings, and also on formatting the data
ready for ingestion and display.

\item In {\bf reconfiguring the site itself} ready for the new data. The
survey team will need to include new Spotter's Guide images and text,
modified tutorial content, and additional survey-specific site content;
the \sw Science Team can help with all of this.

\item In {\bf maintaining the site} so that it continues to function
correctly. This will involve technical support from the Zooniverse team,
but will also require the continued engagement of the wider
collaboration by the Science Team in \Talk. Since this social filter is
a key part of the sample refinement, the latter may involve a
significant time commitment.

>>>>

\sw is a public website. All images displayed there are by definition in the
public domain, and so must be expected to be downloaded, copied and
redistributed by any \sw user. This is a \textbf{good thing}: images of the sky taken
with publicly-funded telescopes belong to everyone.

However, some surveys come with their own proprietary access policy. It is the responsibility
of the SSTs to provide images to \sw in a way that is consistent
with their own data access rules. There are two things that SSTs can
do to in order to respect any proprietary period that they have imposed on
themselves:
\begin{enumerate}

@@

\subsection{Future Project Proposals}
Any future \sw projects are requested to liaise with the PIs regarding their project. We ask that potential project teams first approach the \sw PIs (Marshall, Verma, More collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of their project that includes the following information.

@@

The original \sw papers by definition, provide a complete description of the system, and its results from the CFHTLS survey. The science team of
any other survey (such as DES, RCS, KIDS, PS1, HSC \etc) should be able
to read these papers before designing their own \sw project, and cite them as justification for some of their decisions. As the \sw paper series get published, links to the papers will be given in this draft. Prior to publications, draft papers can also be shared on request by the \sw PIs (\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com})

@@

Implementing a new project based on different survey data will require support from the \sw Science Team, in three respects:

\begin{enumerate}

\item In {\bf preparing data} for the site, and uploading it onto the
Zooniverse servers. There is a reasonable amount of work in preparing data and images by the SSTs for delivery to \sw. The \sw team will provide assistance to SSTs in data preparation. The benefits of using the \sw service will far outweigh the time needed to prepare data.  The \sw Science Team can advise on suitable Training
Subjects and image display settings, and also on formatting the data
ready for ingestion and display.

\item In {\bf reconfiguring the site itself} ready for the new data. The
SST will need to include new Spotter's Guide images and text,
modified tutorial content, and additional survey-specific site content;
the \sw Science Team can help with all of this.

\item In {\bf maintaining the site} so that it continues to function
correctly. This will involve technical support from the Zooniverse and \sw science teams,
but will also require the continued engagement of the wider
collaboration by the SST in \Talk. Since this social filter is
a key part of the sample refinement, the latter may involve a
significant time commitment.
